Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-11-02 paper/amia.tex
Auto Update from local Sharelatex

As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability. To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process. Also included in our GitHub repository are unit tests for KFP using the Python library pytest. Unit tests helped to validate correct functioning of KFP and provides a foundation from which to prevent regressions as new features are added.

@@

KFP provides multiple methods by which a health data scientist can access on-demand faux-data. As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method. The SPA additionally allows for the upload of csv files (not shown) to allow for ease of evaluation and testing of the provided data synthesis methods. Faux-data can either be viewed directly in browser or downloaded in csv format for use in a health data science process. Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query. In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section. Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. This framework is comprised of a provided base class, several examples of plugins, and unit tests for validation purposes. As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

@@

Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed. As shown in the results, some methods are significantly faster than others as dataset size increases. Another key desire is to have synthetic data be as close as possible to real data without compromising individual privacy. While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used. DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset. As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns. The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger input dataset sizes.

>>>>

As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability. To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker \cite{merkel_docker, docker_website} container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process. Also included in our GitHub repository are unit tests for KFP using the Python library pytest. Unit tests helped to validate correct functioning of KFP and provides a foundation from which to prevent regressions as new features are added.

@@

KFP provides multiple methods by which a health data scientist can access on-demand faux-data. As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method. The SPA additionally allows for the upload of csv files (not shown) to allow for ease of evaluation and testing of the provided data synthesis methods. Faux-data can either be viewed directly in browser or downloaded in csv format for use in a health data science process. In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section. The provided Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query. Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively. This Python native API gives full control over all parameters specific each synthesis plugin; the SPA and REST APIs use the default parameters associated with each plugin.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. This framework is comprised of a some base classes and methods that can be extended or overridden, several examples of plugins, and unit tests for validation purposes. As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles ordinal and ratio data yet runs quickly on standard consumer level hardware. Two methods for this plugin are provided: an independent attribute mode where each variable is considered in isolation, and a correlated attribute mode where all variables are evaluated and synthesized together on an observation by observation basis. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

some text \\ and some more text \\ test

\begin{table}
   \caption{Included Data Synthesis Methods}
   \label{included-methods}
   \centering
   \begin{tabular}{p{12em} l p{20em}}
     \toprule
     Method                                 & Source                    & Notes \\
     \midrule
     Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
     DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
     \bottomrule
   \end{tabular}
 \end{table}

@@

Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed. As shown in the results, some methods are significantly faster than others as dataset size increases. Another key desire is to have synthetic data be as close as possible to real data without compromising individual privacy. While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used. DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset. As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns. The DataSynthesizer "Correlated" attribute mode generates more realistic synthetic data than the "Independent" mode as variables in a single observation that are correlated are modeled together. The "Correlated" method does have a significant larger computational burden when generating synthetic data from larger input dataset sizes.
